article

### 2015-12-24 article.rmd
Added new code and dynamic shiny page with query against the tables.

# You do not want clear passwords, but is a sandbox.
con <- dbConnect(MySQL(), 
                 user="msandbox", password="msandbox", port=14901 
                 ,dbname="test", socket="/tmp/mysql_sandbox14901.sock", 
                 host="127.0.0.1")
```

@@

```{r, echo=FALSE}
        ui <- shinyUI(fluidPage(
                mainPanel(textInput("filtering", "FTS Filter:", ""),
                          submitButton("Plot!"),
                          plotOutput("plot")
                          )
        ))
        server <- function(input, output, session) {
                output$plot<-renderPlot({
                        f<-function(x) {eval(parse(text=input$filtering))}
                        x<-1:10
                        plot(x,f(x))
                }                        
                )              
        }

>>>>

# You do not want clear passwords, but is a sandbox.
con <- dbConnect(MySQL(), 
                 user="msandbox", password="msandbox", port=14901 
                 ,dbname="test", socket="/tmp/mysql_sandbox14901.sock", 
                 host="127.0.0.1")

```

@@

```{r, echo=TRUE}
        ui <- shinyUI(fluidPage(
                mainPanel(textInput("filtering", "FTS Filter:", ""),
                          submitButton("Plot!"),
                          plotOutput("plot")
                          )
        ))
        server <- function(input, output, session) {
                output$plot<-renderPlot({
                        f<-function(x) {as.character(input$filtering)}
                        sql <- paste("SELECT source, sum(scoreBoolean), sum(scoreQE),
        max(scoreBoolean),max(scoreQE),
        avg(scoreBoolean), avg(scoreQE),
        avg(lengthContent),
        count(source)
FROM
(
SELECT \"BC\" as source, FTS_DOC_ID, match(BC.content) against (\"" ,f(x) ," \" IN BOOLEAN MODE) as scoreBoolean,
       match(BC.content) against (\""  ,f(x), "\" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION) scoreQE,
       length(content) as lengthContent
FROM
        bookContent BC
WHERE
  match(BC.content) against (\"" ,f(x)," \" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION)
UNION
SELECT \"BL\" as source, FTS_DOC_ID, match(BL.content) against (\"",f(x)," \" IN BOOLEAN MODE) as scoreBoolean,
       match(BL.content) against (\"" ,f(x)," \" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION) scoreQE,
       length(content) as lengthContent
FROM
        bookContentByLine BL
WHERE
  match(BL.content) against (\"", f(x) ,"\" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION)
) unionTable
GROUP BY source
;" , sep = "")
                        rs <- dbGetQuery(con, sql)
                        rs
                        x<-1:10
                        # plot(x,f(x))
                }                        
                )              
        }
